\chapter{HyperBRDF: Neural Generalizable Material Representation}
\label{ch:HyperBRDF}

Appearance is the byproduct of illumination and reflectance, in which the two interact with each other, covering the shape of the objects. Photographs can only capture the appearance with scene components coupled together. Previous chapters discuss appearance manipulations at the image level without any explicit effort for the decomposition of human-distinguishable scene properties. Image-based editing techniques are instrumental in many real-world applications; however, they suffer from the lack of explicit control over scene properties, such as light sources, material types or object geometries. This chapter goes beyond the image-level editing of appearance and brings a physics and graphics aspect to appearance representations. More specifically, it proposes a neural representation of reflectance, which can be incorporated into renderers for photorealistic simulation of the scene appearance.

Bidirectional reflectance distribution functions (\gls{BRDF}) define the reflectance as a function of illumination and viewing directions. This chapter presents HyperBRDF, a technique to estimate measured BRDFs from a sparse set of samples. HyperBRDF offers accurate BRDF reconstructions that are generalisable to new materials. This opens the door to BRDF reconstructions from a variety of data sources. The success of the approach relies on the ability of hypernetworks to generate a robust representation of BRDFs and a set encoder that allows us to feed inputs of different sizes to the architecture. The set encoder and the hypernetwork also enable the compression of densely sampled BRDFs. I evaluate the technique both qualitatively and quantitatively on the well-known MERL dataset of 100 isotropic materials. HyperBRDF accurately 1) estimates the BRDFs of unseen materials even for an extremely sparse sampling, 2) compresses the measured BRDFs into very small embeddings, e.g., 7D. 

\textbf{P.S.} Some figures presented in this chapter are obtained by the co-authors of the corresponding paper. I will include the figures for the completeness of the story, giving credit to them where due. 



\input{Chapters/hyperbrdf-sec/1_introduction}
\input{Chapters/hyperbrdf-sec/2_relatedWork}
\input{Chapters/hyperbrdf-sec/3_method}
\input{Chapters/hyperbrdf-sec/4_experiments}
\input{Chapters/hyperbrdf-sec/5_conclusion}

