\chapter{Introduction}



%\marginpar[Margin note.]{Margin par.}



\section{Overview}
\section{Contributions}
\section{Publications}

The following works are produced throughout my doctoral studies and contributed to main chapters of this dissertation:

\begin{itemize}

\item \textbf{Fazilet Gokbudak}, Alejandro Sztrajman, Chenliang Zhou,  Fangcheng Zhong, Rafal Mantiuk, and Cengiz Oztireli. Hypernetworks for Generalizable BRDF Representation. \textit{ECCV 2024}

\item \textbf{Fazilet Gokbudak and Cengiz Oztireli}. Text-guided Transient Attribute Transfer. \textit{Under review}.

\item \textbf{Fazilet Gokbudak and Cengiz Oztireli}. One-shot Detail Retouching with Patch Space Neural Transformation Blending. \textit{In Proceedings of the 20th ACM SIGGRAPH European Conference on Visual Media Production (CVMP '23)}, 2023. Association for Computing Machinery, New York, NY, USA, Article 2, 1–10. https://doi.org/10.1145/3626495.3626499

\end{itemize}

The following works did not directly contribute to this dissertation; however, they helped me build skills and knowledge for the success of the main contributions:

\begin{itemize}

\item Madeleine Darbyshire, Shaun Coutts, Eleanor Hammond, \textbf{Fazilet Gokbudak}, Cengiz Oztireli, Petra Bosilj, Junfeng Gao, Elizabeth Sklar, and Simon Parsons. Multispectral Fine-Grained Classification of Blackgrass in Wheat and Barley Crops. \textit{Under Review}, 2024.

\item Physically Based Neural Bidirectional Reflectance Distribution Function
Chenliang Zhou, Alejandro Sztrajman, Rainer Gilles, and Fangcheng Zhong, \textbf{Fazilet Gokbudak}, Zhilin Guo, Weihao Xia, Rafal Mantiuk, and Cengiz Oztireli. \textit{Under Review}, 2024.

\end{itemize}

Furthermore, the work I completed during my internship at Amazon 